---
title: "Yelp Capstone"
author: "Peter Blane"
date: "November 22, 2015"
output: html_document
---
# Intro

This project is from the [Yelp Dataset Challenge] (http://www.yelp.com/dataset_challenge). The Yelp Dataset Challenge is a contest that gives a montetary reward to students based on which Yelp judges "submissions on their technical depth and rigor, the relevance of the results to Yelp, our users, or the field, and finally their novelty, uniqueness, and yes, their Yelpy-ness."  

What I have chosen to do is ask the following question about the data: of the businesses that are restaurants, what makes a restaurant with a quiet atmosphere good?

---
# Methods

In order to figure out how to answer the question about quiet restuarants, some exploratory analysis needs to be done to see what types of data is available.

## Reading in the JSON files

After downloading the files, the first thing discovered about the data is that the files are in JSON format.  This is different than the typical data we see in examples (e.g. CSV), so the read method will be:
- Business
```{r}
yelp_business <- "yelp_academic_dataset_business.json"
business <- fromJSON(sprintf("[%s]", paste(readLines(yelp_business), collapse=",")))
```
- Checkin
```{r}
yelp_checkin <- "yelp_academic_dataset_checkin.json"
checkin <- fromJSON(sprintf("[%s]", paste(readLines(yelp_checkin), collapse=",")))
```

- Review
```{r}
yelp_review <- "yelp_academic_dataset_review.json"
review <- fromJSON(sprintf("[%s]", paste(readLines(yelp_review), collapse=",")))
```

- Tip
```{r}
yelp_tip <- "yelp_academic_dataset_tip.json"
tip <- fromJSON(sprintf("[%s]", paste(readLines(yelp_tip), collapse=",")))
```

- User
```{r}
yelp_user <- "yelp_academic_dataset_user.json"
user <- fromJSON(sprintf("[%s]", paste(readLines(yelp_user), collapse=",")))
```

## Exploring the Data

After looking through the files, it became apparent that the "Business" dataset had the information needed to help answer the question.
```{r, results= 'asis'}
unique(business$attributes$`Noise Level`)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
